Extended Data

### 2021-12-03 doc/manuscript/Dow_Extended_Data.Rmd
fix to caption subscripts

![**Extended Data Figure 4 | Response of stem growth phenology and rates to mean maximum temperatures ($T_{max}$) during the spring critial temperature window (CTW) for ring- and diffuse-porous speces at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest.** CTW was defined as the period over which $T_{max}$ was most strongly correlated with the day of year on which 25% of annual growth was achieved ($DOY_{25}$; `r EDT_phenology_parameters`, `r EDF_climwin`). Shown are relationships between mean $T_max$ over the CTW and days of the year on which 25%, 50%, and 75% total stem growth were achieved ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$, respectively; first row); the length of the peak growing season ($L_{pgs}$; second row); maximum growth rate ($g_{max}$; third row); and total seasonal radial stem growth ($\Delta DBH$; fourth row). Posterior predictions of each variable that did not include zero are represented with solid lines, while those that do include zero use dotted lines. 95% credible intervals are represented by bands. For both species groups at both sites, $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$ all declined significantly with mean $T_{max}$ during their respective CTW. Dots represent growth parameter values for individual tree-year combinations, which were derived by fitting a five-parameter logistic growth model to dendrometer band data.](tables_figures/pheno_Tsensitivity_combo_patchwork_AIC.png){ width=90% }

@@

![**Extended Data Figure 5 | Response of stem growth phenology and rates to April mean maximum temperature ($T_{max}$) for ring- and diffuse-porous speces at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest.** Shown are relationships between April $T_max$ and days of the year on which 25%, 50%, and 75% total stem growth were achieved ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$, respectively; first row); the length of the peak growing season ($L_{pgs}$; second row); maximum growth rate ($g_{max}$; third row); and total seasonal radial stem growth ($\Delta DBH$; fourth row). Posterior predictions of each variable that did not include zero are represented with solid lines, while those that do include zero use dotted lines. 95% credible intervals are represented by bands. For both species groups at both sites, $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$ declined significantly with April $T_{max}$, with the exception of $DOY_{25}$ for ring-porous species at SCBI. Dots represent growth parameter values for individual tree-year combinations, which were derived by fitting a five-parameter logistic growth model to dendrometer band data.](tables_figures/pheno_Tsensitivity_combo_patchwork_april.png){ width=90% }

>>>>

![**Extended Data Figure 4 | Response of stem growth phenology and rates to mean maximum temperatures ($T_{max}$) during the spring critial temperature window (CTW) for ring- and diffuse-porous speces at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest.** CTW was defined as the period over which $T_{max}$ was most strongly correlated with the day of year on which 25% of annual growth was achieved ($DOY_{25}$; `r EDT_phenology_parameters`, `r EDF_climwin`). Shown are relationships between mean $T_{max}$ over the CTW and days of the year on which 25%, 50%, and 75% total stem growth were achieved ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$, respectively; first row); the length of the peak growing season ($L_{pgs}$; second row); maximum growth rate ($g_{max}$; third row); and total seasonal radial stem growth ($\Delta DBH$; fourth row). Posterior predictions of each variable that did not include zero are represented with solid lines, while those that do include zero use dotted lines. 95% credible intervals are represented by bands. For both species groups at both sites, $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$ all declined significantly with mean $T_{max}$ during their respective CTW. Dots represent growth parameter values for individual tree-year combinations, which were derived by fitting a five-parameter logistic growth model to dendrometer band data.](tables_figures/pheno_Tsensitivity_combo_patchwork_AIC.png){ width=90% }

@@

![**Extended Data Figure 5 | Response of stem growth phenology and rates to April mean maximum temperature ($T_{max}$) for ring- and diffuse-porous speces at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest.** Shown are relationships between April $T_{max}$ and days of the year on which 25%, 50%, and 75% total stem growth were achieved ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$, respectively; first row); the length of the peak growing season ($L_{pgs}$; second row); maximum growth rate ($g_{max}$; third row); and total seasonal radial stem growth ($\Delta DBH$; fourth row). Posterior predictions of each variable that did not include zero are represented with solid lines, while those that do include zero use dotted lines. 95% credible intervals are represented by bands. For both species groups at both sites, $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$ declined significantly with April $T_{max}$, with the exception of $DOY_{25}$ for ring-porous species at SCBI. Dots represent growth parameter values for individual tree-year combinations, which were derived by fitting a five-parameter logistic growth model to dendrometer band data.](tables_figures/pheno_Tsensitivity_combo_patchwork_april.png){ width=90% }
